Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
wip

We say that the request $(u,v)$ is \emph{external}, if the algorithm that receives this request is in the configuration, where $u$ and $v$ are located at different servers.

We define the algorithm \TAlg in the following way.
\TAlg maintains components for each node.
Intially, each node is in its own singleton component.
For each pair of nodes \TAlg maintains a counter, initiated $0$. 
Upon receiving an external request to a pair, it increases the counter by $1$.
If the counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, in which each component has all of its nodes collocated in one server.
If no such partition exists, \TAlg resets all components to singletons and all counters to $0$ and ends the phase.

>>>>

We say that the request $(u,v)$ is \emph{external}, if the algorithm is in the configuration, where $u$ and $v$ are located at different servers.

We define the algorithm \TAlg in the following way.
\TAlg partition nodes into components.
Intially, each node is in its own singleton component.
For each pair of nodes \TAlg maintains a counter, initiated $0$. 
Upon receiving an external request to a pair, it increases the counter by $1$.
If the counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, in which each component has all of its nodes collocated in one server.
If no such partition exists, \TAlg resets all components to singletons and all counters to $0$ and ends the phase.
